HCI Draft Paper

### 2015-11-30 sigchi-latex-proceedings 2/draft-paper.tex
appendix A & B

>>>>

\section{Appendix}
\section{Appendix A: Participant Tasks}
\textbf{Task Block 1}
\begin{itemize}
\item Task 1: Start at Home Screen. Open Contacts. Find “Ishan Thukral”. Copy his phone number to the clipboard. Switch to Messages.
\item Task 2: In Messages, create a new message. Paste the phone number that you copied. Switch to Photos.
\item Task 3: In Photos, find a photo of a computer. Share this photo to Messages and with Ishan.
\item Task 4: Switch back to Contacts then go to the Home Screen. Stop. Give phone to experimenter.
\end{itemize}

\textbf{Task Block 2}
\begin{itemize}
\item Task 1: Start at Home Screen. Open Email and open the most recent message. Copy the restaurant name from the message body to the clipboard. Switch to Yelp.
\item Task 2: In Yelp, find the restaurant using the name. Copy the address of the restaurant to clipboard. Switch to Google Maps.
\item Task 3: In Google Maps, paste the address as destination. Find out how long it takes you to get there using transit. Switch to Email.
\item Task 4: In Email, reply to the message with the transit time. Go to Home Screen. Stop. Give phone to experimenter.
\end{itemize}

\textbf{Task Block 3}
\begin{itemize}
\item Task 1: Start at Home Screen. Open Internet. Go to m.reddit.com. Tap “Login/Register”. Switch to Notes.
\item Task 2: In Notes, open up note titled “Reddit Login Information”.  Copy the email address. Switch to Internet.
\item Task 3: In Internet, paste the email address in the login screen. Switch to Notes.
\item Task 4: In Notes, copy the password. Switch to Internet.
\item Task 5: In Internet, paste the password. Login to the site. Go to Home Screen. Stop. Give phone to experimenter.
\end{itemize}

\section{Appendix B: Experimental Setup}
\textbf{Task Block 1}
Experimenter opens apps in this order: Messages, Photos.
Task complication: apps won’t be right next to each other when participant opens switcher.

\textbf{Task Block 2}
Experimenter opens apps in this order: Contacts, Yelp, Photos, Google Maps, Messages
Task complication: participants have to find the apps they are switching to in a non-ordered list of open apps.

\textbf{Task Block 3}
Experimenter opens apps in this order: Internet, Google Maps, Yelp, Email, Photos, Messages, Contacts.
Task complication: Participant will have to scroll to the end of the app list to switch to Internet.
